---
title: "How to use routlierutils"
author: "Karanpreet Kaur, Linhan Cai, Qingqing Song"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Here we will demonstrate how to use py_outliers_utils to deal with the outliers in a dataset and plot the distribution of the dataset:

## Libarary package

```{r setup}
library(routliersutils)
```

## Create a dataframe
We need to create a dataframe to work with.

```{r}
df <- data.frame(SepalLengthCm = c(5.1, 4.9, 4.7, 5.5, 5.1, 10, 54, 5.0, 5.2, 5.3, 5.1),
                          SepalWidthCm = c(1.4, 1.4, 10, 2.0, 0.7, 1.6, 1.2, 1.4, 1.8, 1.5, 2.1),
                          PetalWidthCm = c(0.2, 0.2, 0.2, 0.3, 0.4, 0.5, 0.5, 0.6, 0.4, 0.2, 5))
df
```

## Identify outliers
We can identify outliers using `outlier_identifier`. Note that this function will return a dataframe with the summary of the outlier identified by the method, with an additional column having if row has outlier or not if return_df = True.

```{r}
outlier_identifier(df, columns=c('SepalWidthCm',  'PetalWidthCm'), return_df=FALSE)
```
## Trim outliers
We can trim outliers using `trim_outliers`. This function will return a dataframe which the outlier has already process by the chosen method.

```{r}
trim_outliers(df,identifier='IQR', method='trim')
```
## Visualize outliers
We can trim outliers using `visualize_outliers`. This function will return a ggplot of data distribution with given method.

```{r, fig.width=7, fig.height=4}
visualize_outliers(df, columns=c("SepalWidthCm", "PetalWidthCm"), type="violin")
```









